% Chapter Template

\chapter{Reading guide} % Main chapter title

\label{readingGuide} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

This report is targeted at readers with similar knowledge as a student on the 6th semester of
Software Engineering. The report
is divided into 10 main chapters, each split into sections and subsections depending on the content.
Each chapter can be read separately, but it is recommended to read the report in chronological order
to achieve the best possible insight into the project. The report does not contain a profound theoretical
description of the implementation, but explains the final product as it is implemented. It is
recommended to study theoretical parts if the reader is not familiar with used terms.
Chapter one introduces the motivation behind the project, key areas, and an introduction of the company collaborated with. Chapter two describes the problem description and problem statement. Chapter three describe the
requirements of the product and their role throughout the project. Chapter four contains an analysis
of the requirements and presents the domain. Chapter five introduces the design of the
product while Chapter six describes the implementation. In chapter seven validation of the code and validation of the recommendations are provided. Chapter eight discusses how well the system was implemented and what other solution might have been possible. Chapter concludes the project and answers the problem statement. Chapter ten discuss further development of the product and the benefits hereof.\\
All figures in this report will be referenced to as "figure X.Y" where X corresponds to the chapter in
which the figure can be found and Y corresponds to the number of the figure. Figure 4.4 would as an
example refer to figure 4 in Chapter 4. Each figure will include a caption that describes the individual
figures. Chapters and appendices will be referenced as "chapter 4" or "Appendix A". Appendices are found in the back of the report.
All source references are noted with brackets [1], as stated in the IEEE Citation Reference [ieee]. The number
corresponds to the assigned place in the bibliography. All books, websites, articles etc. used can be
found in the Bibliography section at the end of this report.